\section{Conclusions and Future Work}
Current HPC systems are limited in performance and architecture by the the stranding of disaggregated components. In current HPC systems, common tools do not exist to manage increasingly diverse network fabrics and component resources, such as, CPUs, hierarchical memory components, remote NVMe, and accelerators.  Due to lack of access to good Resource Management tools, current HPC systems suffer from inefficient over-design where resources must be provided locally, often in node, to make In instances that HPC running jobs could potentially require the resources.  In addition, the inability to dynamically share available resources, as they are required by running batch jobs can lead to reduced and inefficient computational performance and running job failure.  Centralized resource management can potentially mitigate, out-of-memory conditions, IO thashing, stranding of available resources, such as, CPUs, GPUs, and memories, and provide dynamic network fail-over.  It is clear that Resource Management, using a standardized interface, can enable clients to monitor, compose, and intelligently provision resources, in beneficial ways.

The OpenFabrics Management Framework (OFMF) is a open-source Resource Manager being developed by the OpenFabric Alliance (OFA), the DMTF, SNIA, and the CXL Consortium. The OFMF implements Redfish and Swordfish through the implementation of a Swordfish Endpoint Emulator and network Agents.  The Emulator provides centralized resource monitoring and command control for the attached hardware resources and network fabrics, through matching network Agents. A Composability Manager, integrated with the OFMF, can mitigate stranded resources by providing a method for sharing hardware, CPUs, GPUs, NVM, and memories.  Integration with the OFMF provides the capability for dynamic provisioning of resources to maintain running client computations.  

In this paper, we described the OFMF architecture which enables composing platforms through management of network fabrics, storage fabrics, memory fabrics, and provisioning of GPUs, and CPU components.  The OFMF is designed for configuring fabric interconnects and managing composable disaggregated resources in dynamic HPC infrastructures using client-friendly abstractions.  The goal of the OFMF is to enable interoperability through common interfaces to enable client Managers to efficiently connect workloads with resources in a complex heterogenous ecosystem without having to worry about the underlying network technology.  

We illustrated the composability layer {}, the Redfish RESTful API {}, the OFMF services, and the design of a sample Agent. 

In conclusion, we are developing a solution to enable HPC ecosystems to move from statically defined infrastructure to dynamically defined infrastructure where workload resources can be provisioned depending upon workload needs yto provide the corredct resources to right applications at the right times.

The OFMF is capable of interfacing with multiple fabric managers by means of a set of agents in charge of translating vendor specific APIs into RedFish.


The OFMF is capable of interfacing with multiple fabric managers by means of a set of agents in charge of translating vendor specific APIs into RedFish.
